\documentclass{cover}

\covername{Heber Yesid Daza Toloza}
\coveraddress{Colombia}
\coverphone{(+57) 313 3331900}
\coveremail{heberyesiddazatoloza@gmail.com}
\coverlink{linkedin.com/in/heberdaza}
\recipientname{Hiring Manager}
\recipientcompany{Grip}
\recipientaddress{Colombia}
\coverdate{\today}
\coversubject{Backend Software Engineer}

\begin{document}

\makeheader
\makesubject

\begin{coverbody}
Dear Hiring Team,

I am writing to apply for the Backend Software Engineer position at Grip. Grip's mission to redefine cold-chain logistics for direct-to-consumer eCommerce --- combining advanced technology with a nationwide fulfillment network to optimize perishable goods shipping --- is the kind of data-intensive, systems-level engineering I focus on as a backend developer. The Smart Logistics Engine's ability to analyze over 25 million data points daily to make intelligent, package-level shipping decisions signals the caliber of backend systems I want to build and maintain.

My backend development experience centers on Python, REST APIs, and containerized infrastructure. I built Code Duel, a real-time competitive programming platform featuring a modular Python backend with an isolated runtime layer using Docker containers. The architecture includes WebSocket infrastructure with STOMP/JWT authentication, a matchmaking queue, and a dueling state machine --- demonstrating microservice decomposition and message-driven communication patterns directly applicable to designing scalable APIs and core services at Grip.

I bring hands-on experience with relational databases (PostgreSQL, MySQL), version control (Git), and CI/CD pipelines, paired with a strong engineering foundation in software design patterns, data structures, and algorithms. Across three major projects, I have designed PostgreSQL schemas, built REST APIs, and reduced algorithmic complexity from naive implementations to O(log n). Building real-time systems has required observability thinking --- connection state tracking, error handling, and performance benchmarking --- practices directly applicable to monitoring backend services at scale. I value code reviews and technical design discussions as integral to shipping reliable software.

Grip's technical environment --- backend services in Python and similar languages, PostgreSQL, Docker, and cloud infrastructure --- closely mirrors the stack I have been building with. While my cloud experience to date is with AWS and Google Cloud rather than Azure, the core patterns --- containerized services, managed databases, and CI/CD pipelines --- are platform-agnostic and readily transferable. I am ready to contribute to systems that directly impact supply chain visibility and operational efficiency for DTC brands. I am available immediately and welcome the chance to discuss how my backend engineering experience can contribute to Grip's logistics platform.

Sincerely,\\[1em]
Heber Yesid Daza Toloza
\end{coverbody}

\end{document}
