\documentclass{cover}

\covername{Heber Yesid Daza Toloza}
\coveraddress{Colombia}
\coverphone{(+57) 313 3331900}
\coveremail{heberyesiddazatoloza@gmail.com}
\coverlink{linkedin.com/in/heberdaza}
\recipientname{Hiring Manager}
\recipientcompany{Neostella}
\recipientaddress{Medellin, Antioquia, Colombia}
\coverdate{\today}
\coversubject{Python Developer}

\begin{document}

\makeheader
\makesubject

\begin{coverbody}
Dear Hiring Team,

I am writing to apply for the Python Developer position at Neostella. Based in Colombia, I am particularly drawn to Neostella's growing presence in Medellin and the opportunity to contribute to a platform that is redefining legal technology. Neostella's mission to build connected systems --- bringing together data, workflows, and integrations for modern legal teams --- aligns with my drive to create software that solves real operational challenges. The company's principles of clarity, courage, care, trust, and growth, along with its recognition as a Forbes Best Startup Employer for 2026, signal the kind of environment where I can build meaningful work and grow as an engineer.

My backend development experience centers on Python, REST APIs, and containerized infrastructure. I built Code Duel, a real-time competitive programming platform featuring a modular Python backend with an isolated runtime layer using Docker containers. The system includes WebSocket infrastructure with STOMP/JWT authentication, a matchmaking queue, and a dueling state machine --- demonstrating API design, security patterns, and event-driven architecture directly applicable to Neostella's need for reliable backend services and third-party integrations. I am actively building expertise in serverless architectures and AWS services including Lambda, API Gateway, and Step Functions to complement my existing cloud foundation.

I bring hands-on experience with AWS, CI/CD pipelines, and containerization, paired with a strong engineering foundation in object-oriented programming, SOLID principles, design patterns, and data structures. My professional experience as a Systems Assistant encompassed web development, cloud storage management, and technical infrastructure support --- including technical documentation and cross-functional deliverables. I work within Agile frameworks using Jira and Git, actively seek peer code reviews as a learning mechanism, and respond to feedback as a core part of my development practice. Additionally, my expertise with AI-assisted development tools supports accelerated delivery without sacrificing code quality --- an approach that aligns with Neostella's own investment in AI-powered platform capabilities.

Neostella's technical environment --- Python backend services, AWS cloud infrastructure, REST API integrations, and agile delivery --- closely mirrors the stack I have been building with. With Neostella's offices in Medellin and my immediate availability, I am positioned to contribute from day one. I would welcome the opportunity to discuss how my skills and growth mindset align with Neostella's mission to build the future of legal technology.

Sincerely,\\[1em]
Heber Yesid Daza Toloza
\end{coverbody}

\end{document}
