\documentclass{cover}

\covername{Heber Yesid Daza Toloza}
\coveraddress{Colombia}
\coverphone{(+57) 313 3331900}
\coveremail{heberyesiddazatoloza@gmail.com}
\coverlink{linkedin.com/in/heberdaza}
\recipientname{Hiring Manager}
\recipientcompany{CI\&T}
\recipientaddress{Colombia}
\coverdate{\today}
\coversubject{Mid Level Python Developer}

\begin{document}

\makeheader
\makesubject

\begin{coverbody}
Dear Hiring Team,

I am writing to apply for the Mid Level Python Developer position at CI\&T. With 30 years of technological transformation experience and a team of 8,000 across 25 countries, CI\&T's commitment to AI Deployment and AI-native execution resonates with the direction I am building my career --- combining strong backend engineering with AI-augmented development practices.

My experience centers on Python backend development, including FastAPI, REST APIs, and SQL databases. I built Code Duel, a real-time competitive programming platform with a modular Python backend and Docker-isolated execution layer, applying software design patterns and testing practices throughout. I also developed AulaAlDia, a full-stack school management application that integrated AI tools for predictive analytics --- demonstrating the kind of AI-enhanced solution delivery CI\&T delivers to its enterprise clients.

I bring hands-on experience with SQL (PostgreSQL, MySQL), version control (Git), and software development best practices. I have written custom Python libraries and structured applications using pydantic and SQLAlchemy, with a focus on maintainable, well-tested code. My experience with cloud platforms (AWS, Google Cloud) and CI/CD pipelines provides a foundation for working with Azure-based environments like the one described in this role. I actively seek feedback, participate in code reviews, and work within agile frameworks to meet sprint goals.

As an 8th-semester Systems Engineering student with immediate availability, I am positioned to grow into a long-term contributor at CI\&T. I would welcome the opportunity to discuss how my Python backend skills and AI-augmented development expertise align with CI\&T's mission to turn AI potential into real business impact.

Sincerely,\\[1em]
Heber Yesid Daza Toloza
\end{coverbody}

\end{document}
