\documentclass[11pt,a4paper]{moderncv}

% ----- style & color -----
\moderncvstyle{banking}
\moderncvcolor{blue}

% ----- fonts (lualatex, fallback-safe) -----
\usepackage{fontspec}
\IfFontExistsTF{Lato}{\setsansfont{Lato}}{}
\IfFontExistsTF{Raleway}{\setsansfont{Raleway}}{}

% ----- layout -----
\usepackage[scale=0.75,top=0.6cm,bottom=0.6cm]{geometry}
\setlength{\hintscolumnwidth}{3cm}

% allow underscores in text
\catcode`\_=12

% ----- personal data -----
\firstname{Heber Yesid}
\familyname{Daza Toloza}
\title{Backend Software Engineer}
\address{}{Colombia}
\mobile{(+57) 313 3331900}
\email{heberyesiddazatoloza@gmail.com}
\social[linkedin]{heberdaza}
\social[github]{heberdaza}
\homepage{heberdaza.dev}

\begin{document}
\makecvtitle

% ----- profile summary -----
\section{Professional Summary}
\cvline{}{Backend developer with experience in Python, Java, REST API design, and relational databases. Built scalable systems using Docker, CI/CD pipelines, and cloud services. Strong foundation in OOP, data structures, and software design patterns. Experience with microservice decomposition, message-driven communication, and containerized runtimes. Seeking to contribute to Grip's logistics platform as a Backend Software Engineer.}

% ----- experience -----
\section{Experience}

\cventry{Jun 2024 -- Feb 2025}{Systems Assistant}{[Employer]}{Colombia}{}{%
Developed and maintained web applications and backend services using Python. Provided technical support, maintained cloud storage infrastructure, and enforced information security protocols. Produced technical documentation and collaborated with cross-functional teams.
}

\cventry{2024 -- 2025}{Code Duel -- Competitive Programming Platform}{Personal Project}{}{}{%
Built a real-time coding challenge platform with a modular Python backend and isolated runtime layer using Docker containers. Implemented WebSocket infrastructure with STOMP/JWT authentication, a matchmaking queue, and a dueling state machine --- demonstrating microservice decomposition, message-driven communication, and API design patterns applicable to distributed backend systems.
}

\cventry{2024}{Concurrent Scheduler -- Process Simulator}{Personal Project}{}{}{%
Designed a process scheduling system with dynamic prioritization and aging. Optimized task selection to O(log n) complexity using multilevel priority queues. Validated correctness with jqwik property tests and JMH benchmarks --- applying TDD-adjacent testing practices to ensure system reliability.
}

\cventry{2024}{AulaAlDia -- Intelligent Academic Management}{Personal Project}{}{}{%
Developed a full-stack school management application with integrated AI tools. Built REST APIs for automatic grade calculation, predictive analytics, and a visual alert system. Designed relational database schemas in PostgreSQL for academic data management.
}

% ----- education -----
\section{Education}
\cventry{2022 -- Present}{Systems Engineering}{University of Santander}{Colombia}{8th Semester (In Progress)}{}

% ----- skills -----
\section{Skills}
\cvitem{Languages \& Frameworks}{Python (Django, FastAPI), Java (Spring Boot)}
\cvitem{Databases}{PostgreSQL, MySQL, MongoDB, Redis}
\cvitem{APIs \& Communication}{REST APIs, WebSocket (STOMP), JWT}
\cvitem{Cloud \& DevOps}{AWS, Google Cloud, Docker, CI/CD, Git, GitHub}
\cvitem{AI Tools}{Claude Code, Codex -- Skills, MCP, prompt engineering}
\cvitem{Methodologies}{Agile (Scrum), Jira, Trello}
\cvitem{Engineering}{SOLID, design patterns, data structures, algorithms, microservices}

% ----- languages -----
\section{Languages}
\cvlanguage{Spanish}{Native}{}
\cvlanguage{English}{Conversational}{Technical communication -- English for IT 1 \& 2 (Cisco)}

% ----- certifications -----
\section{Certifications}
\cvline{2024}{Python Essentials I \& II -- Cisco Networking Academy}
\cvline{2024}{Advanced Programming Bootcamp -- Talento Tech Colombia}
\cvline{2024}{English for IT 1 \& 2 -- Cisco Networking Academy}

\end{document}
